%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{graphicx}
\graphicspath{ {./images/} }
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \text{\small#3} & \text{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \text{\small#1} & \text{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
 %\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://rajkumaar.co.in/}{\Large Rajkumar Sukumar}} & Email : \href{mailto:rajkumaar2304@icloud.com}{rajkumaar2304@icloud.com}\\
%   \href{https://rajkumaar.co.in/}{\underline{https://www.rajkumaar.co.in}} & Mobile : +1-602-768-7075\\
%  \end{tabular*}

\begin{center}
    \textbf{{\Huge Rajkumar Sukumar}} \\ \vspace{6pt}
    \small \raisebox{-0.1\height}\faPhone\ \href{tel://+16027687075}{+1-602-768-7075} ~ \href{mailto:rajkumaar2304@icloud.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{rajkumaar2304@icloud.com}} ~ 
    \href{https://rajkumaar.co.in}{\raisebox{-0.2\height}\faGlobe\ \underline{rajkumaar.co.in}}  ~
    \href{https://github.com/rajkumaar23}{\raisebox{-0.2\height}\faGithub\ \underline{rajkumaar23}}  ~
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
      \resumeSubheading  {Arizona State University}{August 2022 -- May 2024} {Master of Science in Computer Science $|$ {GPA : 3.56/4.0}} {Tempe, AZ}
    \resumeSubheading  {Amrita Vishwa Vidyapeetham}{July 2017 -- June 2021} {Bachelor of Technology in Computer Science and Engineering $|$ {GPA : 8.57/10.0}} {Coimbatore, India}
  \resumeSubHeadingListEnd
  

%-----------EXPERIENCE-----------
\section{Experience}

  \resumeSubHeadingListStart

    \resumeSubheading
      {CodeChef (Unacademy Group)}{May 2020 -- July 2022}
      {Application Engineer $|$ Prev. Intern $|$ Tech : PHP,  Python,  ReactJS,  MySQL, SaltStack, AWS}{Bangalore, India}
      \resumeItemListStart
        \resumeItem{\textbf{Mashups} - Designed a portal for users to create their \href{https://www.codechef.com/mashup-contest}{\underline{private contests}} with problems of their choice.}        
        \resumeItem{\textbf{Contest Management} - Migrated the entire \href{https://www.codechef.com/hostyourcontest/}{\underline{"host your contest"}} portal written in EmberJS to ReactJS.}
              \resumeItem{\textbf{Site Manager} - Built a CLI tool using PHP and integrated it with Nginx to manage the sites during maintenance.}
              \resumeItem{\textbf{DevOps} - Integrated GitHub action pipelines for tasks including release-notes generation, code linting, and unit testing.}
              \resumeItem{\textbf{Security} - Mitigated various security vulnerabilities ranging from XSS to SQL injections.}
      \resumeItemListEnd
      
          \resumeSubheading
      {Internshala}{June 2018 -- May 2020}
      {Teaching Assistant $|$ Tech: C, C++}{Remote}
      \resumeItemListStart
        \resumeItem{Demystified technical queries of students,  evaluated assignments, and upgraded the training content.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Anokha (Amrita University's Tech-fest)}{November 2019 -- February 2020}
      {Head of the Software Team $|$ Tech: Laravel,  MySQL,  NuxtJS,  Angular8,  CentOS}{Coimbatore, India}
      \resumeItemListStart
        \resumeItem{Managed a \textbf{team of 10} in building and delivering a suite of applications essential for organizing the tech-fest.}
        \resumeItem{The apps included a mobile-friendly PWA based on NuxtJS,  an android app,  an API service built using Laravel,  and an administration portal built with Angular 8.}
    \resumeItemListEnd    
    
    \resumeSubheading
      {PSG Software Technologies}{May 2019 -- June 2019}
      {Mobile App Developer Intern $|$ Tech : NodeJS,  NativeScript}{Coimbatore, India}
      \resumeItemListStart
        \resumeItem{Devised and delivered a cross-platform mobile application using NativeScript,  for maintaining the health profiles of families in community areas of PSG Urban Health Centre.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Amrita Repository} $|$ \text{Android, SQLite, Web Scraping, PHP, Python} $|$ \href{https://github.com/rajkumaar23/amrita-repository}{\underline {GitHub Link}}}{}
          \resumeItemListStart
            \resumeItem{Engineered an android application and a telegram bot for my peers to avail old question papers, timetables,  etc., which has received over \textbf{10,000} downloads in the Google Play Store,  with an average of \textbf{4000} monthly active users.}
            \resumeItem{Received a letter of appreciation from the Dean of Engineering for making students' academic lives easier.}
          \resumeItemListEnd
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Flowgramming} $|$ \text{HTML, Bootstrap, jQuery,  JointJS} $|$ \href{https://flowgrammers-org.github.io/flowgramming/}{\underline{Application Link}}}{}
          \resumeItemListStart
            \resumeItem{Built a progressive web application,  as an efficient alternative to Flowgorithm,  to design and execute flowcharts,  with the support for all basic programming constructs,  including but not limited to user-defined functions and 2D arrays.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Amrita Wallet} $|$ \text{Android, NodeJS, MongoDB, VueJS}}{}
          \resumeItemListStart
            \resumeItem{Standardized payments across the university including cafeterias, by replacing cash with rechargeable student ID cards,  with nearly \textbf{5000} active cards as of date.}          
            \resumeItem{Developed an android app for scanning cards and making payments,  with the help of a centralized NodeJS server on top of a MongoDB cluster added with an admin portal built using VueJS for monitoring.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Campus Management System} $|$ \text{PHP, Laravel, MySQL, Android} $|$ \href{https://cms.cb.amrita.edu/humans.txt}{\underline{Website Link}}}{}
          \resumeItemListStart
            \resumeItem{Contributed REST APIs in Laravel and an Android app to the system, which is used by security guards and monitored by the college authorities for tracking students' day-to-day access to campus.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    \textbf{Areas of Interest}{: Full Stack Development, Cyber Security} \\
     \textbf{Languages and Frameworks}{: C++, PHP, Java, JavaScript, SQL, Python, Android, Node.js, Angular, ReactJS, Laravel} \\
     \textbf{Tools and Technologies}{: AWS, Docker, Apache2, Nginx, Jenkins, SaltStack} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Awards / Extracurricular}
            \resumeItemListStart
                        	\resumeItem{Worked as a Tutor at McClintock High School in Tempe as part of the AZ-R3 program by Access ASU.}\vspace{-5pt}
            	\resumeItem{Received the prestigious \textbf{Outstanding Project Award} for Flowgramming from Amrita School of Engineering.}\vspace{-5pt}
                \resumeItem{Secured \textbf{{$2^{nd}$} position} out of 30 teams in a polyglot coding contest, during Anokha Tech-fest 2020.}\vspace{-5pt}
                \resumeItem{Received bug bounties from various organisations for reporting critical security vulnerabilities.}\vspace{-5pt}
                \resumeItem{Conducted workshops for 50+ students as the Head of Android at Developer Student Clubs by Google Developers.}\vspace{-5pt}
            \resumeItemListEnd


\end{document}
