%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{graphicx}
\graphicspath{ {./images/} }
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
\usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \text{\small#3} & \text{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \text{\small#1} & \text{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://rajkumaar.co.in/}{\Huge Rajkumar S}} & Email : \href{mailto:rajkumaar2304@icloud.com}{rajkumaar2304@icloud.com}\\
%   \href{https://rajkumaar.co.in/}{https://rajkumaar.co.in} & Mobile : +91-759-290-3711\\
%  \end{tabular*}

\begin{center}
    \textbf{{\Huge Rajkumar S}} \\ \vspace{6pt}
    \small \raisebox{-0.1\height}\faPhone\ \href{tel://+917592903711}{+91-75929-03711} ~ \href{mailto:rajkumaar2304@icloud.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{rajkumaar2304@icloud.com}} ~ 
    \href{https://rajkumaar.co.in}{\raisebox{-0.2\height}\faGlobe\ \underline{rajkumaar.co.in}}  ~
    \href{https://github.com/rajkumaar23}{\raisebox{-0.2\height}\faGithub\ \underline{rajkumaar23}}  ~
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading  {Amrita Vishwa Vidyapeetham, Coimbatore}{July 2017 -- June 2021} {Bachelor of Technology in Computer Science and Engineering} {CGPA: 8.57/10}
  \resumeSubHeadingListEnd
  

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {CodeChef (Unacademy Group)}{May 2020 -- Present}
      {Application Engineer $|$ Ex. Intern $|$ Tech : PHP,  ReactJS,  MySQL, SaltStack, AWS}{Bangalore, Karnataka}
      \resumeItemListStart
              \resumeItem{Mitigated and fixed various security vulnerabilities from reports of our Bug Bounty Program.}
        \resumeItem{Optimised various SQL queries upto a maximum of \textbf{10x}, which had caused performance bottlenecks during peak traffic.}
        \resumeItem{Built necessary REST APIs and revamped the entire \href{https://www.codechef.com/hostyourcontest/}{\underline{Host Your Contest}} portal, used by contest managers, to ReactJS.}
      \resumeItemListEnd

    \resumeSubheading
      {Internshala}{June 2018 -- May 2020}
      {Teaching Assistant $|$ Tech: C/C++}{Remote}
      \resumeItemListStart
        \resumeItem{Demystified technical queries of students,  evaluated assignments and provided feedback.}
        \resumeItem{Helped in upgrading the training content at \href{https://trainings.internshala.com}{https://trainings.internshala.com}.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Anokha (Amrita University's Techfest)}{Nov 2019 -- Feb 2020}
      {Head of the Software Team $|$ Tech: Laravel,  MySQL,  NuxtJS,  Angular8,  CentOS}{Coimbatore, Tamilnadu}
      \resumeItemListStart
        \resumeItem{Managed a \textbf{team of 10} in building and delivering a suite of applications essential for organising the techfest.}
        \resumeItem{The apps included a mobile-friendly PWA based on NuxtJS,  an android app,  an API service built using Laravel,  and an administration portal built using Angular8.}
    \resumeItemListEnd    
    
    \resumeSubheading
      {PSG Software Technologies}{May 2019 -- June 2019}
      {Mobile App Developer Intern $|$ Tech : NodeJS,  NativeScript}{Coimbatore, Tamilnadu}
      \resumeItemListStart
        \resumeItem{Devised and delivered a cross-platform mobile application using NativeScript,  for maintaining the health profiles of families in community areas of PSG Urban Health Centre.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Amrita Repository} $|$ \text{Android, SQLite, Web Scraping, PHP} $|$ \href{https://github.com/rajkumaar23/amrita-repository}{\underline {Repository Link}}}{}
          \resumeItemListStart
            \resumeItem{Engineered an android application and a telegram bot for my peers to avail old question papers, timetables,  etc.  which has received \textbf{7200+} downloads in Play Store,  with an average of \textbf{4000} monthly active users.}
            \resumeItem{Received a letter of appreciation from the Dean of Engineering for making the academic lives of students easier.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Amrita Wallet} $|$ \text{Android, NodeJS, MongoDB, jQuery, PM2}}{}
          \resumeItemListStart
            \resumeItem{Developed an android app for scanning cards and making payments,  with the help of a centralised NodeJS server on top of a MongoDB cluster added with an admin portal built using VueJS for monitoring.}          
            \resumeItem{Standardised payments across the university including cafeterias by replacing cash with ID cards,  that are rechargeable at stations around the campus,  with \textbf{3000+} active cards as on date.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Campus Management System} $|$ \text{PHP, Laravel, MySQL, Android} $|$ \href{https://cms.cb.amrita.edu/humans.txt}{\underline{Website Link}}}{}
          \resumeItemListStart
            \resumeItem{Contributed REST APIs in Laravel and an Android app to the system which notably tracks day-to-day entry/exit of students from campus,  is used by security guards and monitored by the college authorities.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Flowgramming} $|$ \text{HTML, Bootstrap, jQuery,  JointJS} $|$ \href{https://flowgrammers-org.github.io/flowgramming/}{\underline{Application Link}}}{}
          \resumeItemListStart
            \resumeItem{Built a progressive web application,  as an efficient alternative to Flowgorithm,  to design and execute flowcharts,  with the support for all basic programming constructs,  including but not limited to user defined functions and 2D arrays.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, PHP, Java, HTML/CSS, JavaScript, SQL, Python, with the ability to learn any language required.} \\
     \textbf{Technologies/Frameworks}{: Android, Laravel, Angular, ReactJS, NodeJS, Docker, Apache2/Nginx} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Awards / Extracurricular}
            \resumeItemListStart
                \resumeItem{Secured 2nd position out of 30 teams in PolyCodeGlot, during Anokha 2020.}\vspace{-5pt}
                \resumeItem{Secured 4th position out of 140 participants in NJACK Winter of Code 2019, organised by IIT-Patna.}\vspace{-5pt}
                \resumeItem{Received bug bounties worth 50,000 INR from various organisations for reporting criticial vulnerabilities.}\vspace{-5pt}
                \resumeItem{Conducted various workshops as the Head of Android, at Developer Student Club powered by Google Developers,  wherein 50+ students from all branches of engineering got benefited.}\vspace{-5pt}
            \resumeItemListEnd


\end{document}
