%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \text{\small#3} & \text{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \text{\small#1} & \text{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Rajkumar S} \\ \vspace{6pt}
    \small \raisebox{-0.1\height}\faPhone\ +91-7592903711 ~ \href{mailto:rajkumaar2304@icloud.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{rajkumaar2304@icloud.com}} ~ 
    \href{https://rajkumaar.co.in}{\raisebox{-0.2\height}\faGlobe\ \underline{rajkumaar.co.in}}  ~
    \href{https://github.com/rajkumaar23}{\raisebox{-0.2\height}\faGithub\ \underline{rajkumaar23}}  ~
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading  {Amrita Vishwa Vidyapeetham, Coimbatore}{July 2017 -- June 2021} {Bachelor of Technology in Computer Science and Engineering} {CGPA: 8.51/10}
  \resumeSubHeadingListEnd

% %------RELEVANT COURSEWORK-------
% \section{Relevant Coursework}
%     %\resumeSubHeadingListStart
%         \begin{multicols}{4}
%             \begin{itemize}[itemsep=-5pt, parsep=3pt]
%                 \item\small Data Structures
%                 \item Software Methodology
%                 \item Algorithms Analysis
%                 \item Database Management
%                 \item Artificial Intelligence
%                 \item Internet Technology
%                 \item Systems Programming
%                 \item Computer Architecture
%             \end{itemize}
%         \end{multicols}
%         \vspace*{2.0\multicolsep}
%     %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {CodeChef (Unacademy Group)}{May 2020 -- Present}
      {Software Engineer Intern}{Bangalore, Karnataka}
      \resumeItemListStart
        \resumeItem{Contributed to CCDSAP, HYC, fixed bugs from Bug Bounty Program and optimised SQL queries by 10x.}
      \resumeItemListEnd

    \resumeSubheading
      {Internshala}{June 2018 -- May 2020}
      {C/C++ Virtual Teaching Assistant}{Remote}
      \resumeItemListStart
        \resumeItem{Demystified technical queries of students, evaluated assignments and provided feedback.}
        \resumeItem{Helped in upgrading the training content at https://trainings.internshala.com.}
    \resumeItemListEnd
    
    \resumeSubheading
      {Anokha (Amrita University's Techfest)}{Nov 2019 -- Feb 2020}
      {Head of the Software Development Team}{Coimbatore, Tamilnadu}
      \resumeItemListStart
        \resumeItem{Managed a team of 10, gained exposure to MVC & Eloquent ORM, contributed to building REST APIs, and integrated push notifications with the help of Firebase.}
        \resumeItem{Developed an android app for the techfest and a panel website based on Angular 8, from scratch along with the team.}
    \resumeItemListEnd    
    
    \resumeSubheading
      {PSG Software Technologies}{May 2019 -- June 2019}
      {Mobile App Developer Intern}{Coimbatore, Tamilnadu}
      \resumeItemListStart
        \resumeItem{Devised a cross platform mobile app using NativeScript, for maintaining health profiles of
families in community areas of PSG Urban Health Centre, and delivered the product.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Amrita Repository} $|$ \text{Android, SQLite, Web Scraping, PHP}}{}
          \resumeItemListStart
            \resumeItem{Engineered an android app for my fellow college students to avail old question papers,
timetables, exam schedules, attendance, grades with OTP based login and much more.}
            \resumeItem{As on date, the app has received 7200+ downloads in Play Store, with an average of 4000 monthly
active users.}
            \resumeItem{ Received a letter of appreciation from the Dean of engineering department.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{Amrita Wallet} $|$ \text{Android, NodeJS, MongoDB, jQuery, PM2}}{}
          \resumeItemListStart
            \resumeItem{Standardised payments across the university including cafeterias by replacing cash with ID cards, with
recharge stations around the campus, with 2000+ users as on date.}
            \resumeItem{Implemented a suite of apps including an android app for scanning cards and making payments,
with the help of a centralised NodeJS server on top of a MongoDB cluster added with an
Admin Panel built using VueJS for monitoring.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{Campus Management System} $|$ \text{PHP, Laravel, MySQL, Android}}{}
          \resumeItemListStart
            \resumeItem{Amrita CMS notably tracks day-to-day entry/exit of students from campus, is used by
security guards and monitored by the college authorities.}
            \resumeItem{Contributed REST APIs and an Android app (Play Store Link) to the system, with the help
of university’s official IT Team.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, PHP, Java, HTML/CSS, JavaScript, SQL} \\
     \textbf{Technologies/Frameworks}{: Android, Laravel, Angular, ReactJS, NodeJS, Docker, Apache2/Nginx, Bootstrap, Drupal} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Awards / Extracurricular}
    \resumeSubHeadingListStart
            \resumeItemListStart
                \resumeItem{Secured 2nd position out of 30 teams in PolyCodeGlot, during Anokha 2020.}
                \resumeItem{Secured 4th position out of 140 in NJACK Winter of Code 2019, organised by IIT-Patna.}
                \resumeItem{Assisted school kids at a workshop conducted by Mango Education, Coimbatore to learn Android App Development using the tool, MIT App Inventor.}
                \resumeItem{Conducted various workshops as Head of Android, Developer Student Club powered by Google Developers , wherein 50+ students from all branches of engineering got benefited.}
            \resumeItemListEnd
    \resumeSubHeadingListEnd


\end{document}
